Beyesian Inference for Decision Making under COVID-19: A case study

### 2020-05-31 out/paper.Rmd
Correción de número de pie de página duplicado

The frequentist approach, as powerful as it is, may not be the best choice for a setting such the one we are facing now a days[^8]. **CONLUIR**

[^8]: Besides many authors as Mendoza (**INSERTAR AÑO**) have documented many issues with the classical procedures such as failures in the construction of confidence intervals [see](insertar link)

>>>>

The frequentist approach, as powerful as it is, may not be the best choice for a setting such the one we are facing now a days[^9]. **CONLUIR**

[^9]: Besides many authors as Mendoza (**INSERTAR AÑO**) have documented many issues with the classical procedures such as failures in the construction of confidence intervals [see](insertar link)
